Figures for Paper

### 2021-03-18 paper_figures.Rmd
updated tables and script
added two samples for each condition to gain significance - added statistical analysis on script and figures

---
title: "Figures for Paper"
author: "Anna-Leigh Brown + Matteo Zanovello"
date: "06/10/2020"
output: 
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
---

@@

for_bar_plot_sy <- read_csv(file.path(here::here(),"data","results_17022021_sy5y.csv"))

for_bar_plot_sy <- data.frame(for_bar_plot_sy)
for_bar_plot_sy$condition <- as.factor(for_bar_plot_sy$condition)
for_bar_plot_sy$condition <- factor(for_bar_plot_sy$condition,levels(for_bar_plot_sy$condition)[c(2,1)])

nmd_plot = ggbarplot(for_bar_plot_sy,
                        x = 'gene',
                        add = c("mean_se","jitter"),
                        y = 'value',
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) + 
  scale_y_continuous(labels = scales::percent) + 
  ggpubr::theme_pubr() +
  scale_fill_manual(
    values = c("#40B0A6","#E1BE6A")
  ) + 
  scale_color_manual(
    values = c("#1C2617","#262114")
  )

plot(nmd_plot)
```

>>>>

---
title: "Figures for Paper"
author: "Anna-Leigh Brown"
date: "06/10/2020"
output: 
    html_document:
        code_folding: hide
        toc: true
        toc_float: true
---

@@

fbp_sy <- read_csv(file.path(here::here(),"data","results_17022021_sy5y.csv"))
fbp_sy$condition <- as.factor(fbp_sy$condition)
fbp_sy$condition <- factor(fbp_sy$condition,levels(fbp_sy$condition)[c(2,1)])

stattest_sy <- fbp_sy %>%
    group_by(gene) %>%
    t_test(value ~ 1, mu = 1) %>%
    add_significance() %>%
    add_xy_position(x="gene")
stattest_sy

nmd_plot_sy <- ggbarplot(fbp_sy,
                     x = 'gene',
                     y = 'value',
                     add = c("mean_se","jitter"),
                     fill = 'condition',
                     color = 'condition',
                     position = position_dodge(0.8),
                     dot.size = 10) +
    scale_y_continuous(labels = scales::percent) + 
    ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("#40B0A6","#E1BE6A")) + 
    scale_color_manual(values = c("#1C2617","#262114")) +
    ylab("Percent of transcript after CHX treatment") +
    xlab("") +
    stat_pvalue_manual(stattest_sy, label="p.signif", y.position = 9)
nmd_plot_sy

fbp_dz <- read_csv(file.path(here::here(),"data","results_17022021_dz.csv"))
fbp_dz$condition <- as.factor(fbp_dz$condition)
fbp_dz$condition <- factor(fbp_dz$condition,levels(fbp_dz$condition)[c(2,1)])

stattest_dz <- fbp_dz %>%
    group_by(gene) %>%
    t_test(value ~ 1, mu = 1) %>%
    add_significance() %>%
    add_xy_position(x="gene")
stattest_dz

nmd_plot_dz <- ggbarplot(fbp_dz,
                        x = 'gene',
                        y = 'value',
                        add = c("mean_se","jitter"),
                        fill = 'condition',
                        color = 'condition',
                        position = position_dodge(0.8),
                        dot.size = 10) +
    scale_y_continuous(labels = scales::percent) + 
    ggpubr::theme_pubr() + 
    scale_fill_manual(values = c("#40B0A6","#E1BE6A")) + 
    scale_color_manual(values = c("#1C2617","#262114")) +
    ylab("Percent of transcript after CHX treatment") +
    xlab("") +
    stat_pvalue_manual(stattest_dz, label="p.signif", y.position = 26)
nmd_plot_dz
